|

### 2018-12-18 Paper 2019.Rmd
Panel tables to pull from. Does any of this go in the paper? Appendices?

```{r output to table?}

### Model II: Difference-in-Difference Model
<!--Add specification, formulas?-->
Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption. A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant. If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.

@@

\newpage 
```{r stargzer CCI html}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="text", 
  title = "Are campaign limits and corruption convictions correlated?",
  out="collateral/CCI.htm",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

\newpage
\blandscape
```{r stargazer DiD latex, results="asis", eval=TRUE}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  title = "Do changes in limits lead to lower levels of corruption?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
  font.size = "small", 
  header = FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2,
  no.space = TRUE)

@@

```
old code -->

>>>>

```{r CCI output to table}
stargazer(cci.base.pooled, 
          cci.limits.pooled, 
          cci.limits.fixed,
          cci.limits.fixed.time, 
          type="text",
          title = "Are the presence or amounts of campaign limits correlated with corruption convictions?",
          out="collateral/CCI.htm",
          dep.var.labels = "Corruption Convictions Index",
          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
          )
```

```{r CRI output to table}
stargazer(cri.base.pooled, 
          cri.limits.pooled, 
          cri.limits.fixed,
          cri.limits.fixed.time, 
          type="text",
          title = "Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
          out="collateral/CRI.htm",
          dep.var.labels = "Corruption Convictions Index",
          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
          )
```
### Model II: Difference-in-Difference Model
<!--Add specification, formulas?-->
Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption. A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant. If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.

@@

@@

```{r stargzer CCI html}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="text", 
  title = "Are campaign limits and corruption convictions correlated?",
  out="collateral/CCI.htm",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

\blandscape
```{r stargazer DiD latex, results="asis", eval=TRUE}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  title = "Do changes in limits lead to lower levels of corruption?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
  font.size = "small", 
  header = FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2,
  no.space = TRUE)

old code -->
